---
title: "Session4"
author: "Omotolani Ligali"
date: "10/31/2019"
output:
  word_document: default
  pdf_document: default
---

#QUESTION 1: One sample t-test

#Answer:

#Hypothesis

#Null Hypothesis: The mean is equal to 0.4

#Alternate Hypothesis: The mean is greater than  0.4

#Level of Significance: The level of significance is 0.05

#Test:
```{r}
dt<-read.csv("data/diamond.csv",header = T)
carat<-t.test(dt$carat,mu = 0.4,alternative = "greater")
carat
```
#Conclusion: Since the p-value from the test is less than 0.05,the null hypothesis is rejected and the true mean is greater than 0.4 

#QUESTION 2: Two sample independent T-test

#Answer:

#Hypothesis

#Null Hypothesis: The difference in mean of group M and group B is equal to zero

#Alternate Hypothesis: The difference in mean of group M and group B is not equal to zero

#Level of Significance: The level of significance is 0.05

#Test:
```{r}
ct<-read.csv("data/cancer.csv",header = T)
t.test(ct$area_worst~ct$diagnosis,alternative ="two.sided")
```
#Conclusion: Since the p-value from the test is less than 0.05, the null hypothesis is rejected,and the true difference in mean is not equal to zero

#QUESTION 3:Two sample paired test

#Answer:

#Hypothesis

#Null Hypothesis: The difference in mean of tumor size before treatment and tumor size after treatment is equal to zero

#Alternate Hypothesis: The difference in mean of tumor size before treatment and tumor size after treatment is not equal to zero

#Level of Significance: The level of significance is 0.05

#Test:
```{r}

tumor<-c(80, 45, 78, 89, 80, 90, 91, 89, 56, 78, 89,81)
```
```{r}

tumor1<-c(61, 71, 62, 78, 88, 71, 78, 79, 67, 66,78,79)
```
```{r}
t.test(tumor,tumor1,paired = TRUE)
```
#Conclusion: Since the p-value from the test is greater than our level of significance, therefore the null hypothesis is not rejected